


\part{Appendices}
\appendix

\chapter{Differences between version 1.2 and 1.3}

\section{Users}
\label{sec:DifferencesUsers}

The way users are defined and used differs greatly between LedgerSMB 1.3 and
older versions. In version 1.3 user access to the database is enforced by the
database itself. This means that users logging in to the LedgerSMB web application
are in reality logging into the PostgreSQL database. In older versions, the web
app would verify the user's credentials (using a common database connection used
for all users).

The difference between these approaches is that security is no longer (solely)
maintained by the web application - with all inherent risks. Instead, the database
now plays an important role as well. The effect is that the LedgerSMB team now
leverages the experience of the PostgreSQL community - a highly respected community
well known for its security focus - to make sure your data stays secure.

This structure also enables LedgerSMB 1.3 to offer separation of duties and
authorizations throughout the application without being required to do a full
rewrite of the application.

It's this shift in paradigm that makes it impossible to meaningfully migrate
users from older LedgerSMB and SQL-Ledger versions to LedgerSMB 1.3.


\chapter{Migration}

\section{Introduction}

There are plenty of reasons to want to migrate to LedgerSMB 1.3:

\begin{enumerate}
\item Separation of duties
\item Security better integrated into the application
\item Better, more strict data model
\label{item:StricterDataModel}
\item Some important sources of user error eliminated
\item Better workflows for cash reconciliation
\item @@@ others?
\end{enumerate}

Yet, while item \ref{item:StricterDataModel} is a good reason to want to switch, it's
also a reason why migration from older versions to 1.3 can be harder than earlier
migrations: when the data
in your older version is not consistent, it won't fit into the new data model and
will need to be fixed first.

Especially if your database has a very long line of history, being migrated trough
lots of SQL-Ledger and LedgerSMB versions, you may want to consider asking for help
from a professional party. It could save you a lot of time.

However, don't be discouraged and have a go yourself first. Just be sure to run
your upgrade on a backup database: the migration process is non-destructive, but
in case accounting data is involved: better safe than sorry!

Also it is worth noting that a number of automatic checks are performed on your
data prior to migration, and to the extent possible, you are given an
opportunity to fix those issues identified.  Because these checks are
pre-migration checks, they are written to your old data and will persist after
backing out of a migration to 1.3.

\section{From older LedgerSMB versions}

\section{From SQL-Ledger 2.8}

\section{From older SQL-Ledger versions}

\section{From other accounting packages}

While accounting and ERP solution have wildly differing structures to record their
data, this sections uses data with a relatively simple structure as a show case of
how this problem may be dealt with.

\begin{quote}
Note that the encoding you use to transfer to the database depends on the settings
used to create the PostgreSQL database with.  A migration is a good moment to think
about encodings an solve older encoding issues.  Now would be a good moment to
anticipate the requirement for accented characters and non-western alphabets: set up
a UTF-8 encoded database and recode your data accordingly.
\end{quote}

\subsection{Migrating customers}

The source system for this section uses a structure where every company has one
contact person, one address, one phone number and e-mail.

In order to understand how to migrate this data structure to LedgerSMB, it's
important to understand that:

\begin{enumerate}
\item The company from the source maps to the \emph{Company} and \emph{Entity} entities
\item The contact person maps to the \emph{Entity Credit Account} entity
\item The address maps to the \emph{Location} entity - and requires a location class: Sales, Billing or Shipping
\item The phone number, fax number and e-mail map to \emph{Contact items}
\end{enumerate}

The reason behind the separation between the \emph{Company} and \emph{Entity} entities
is that every customer is an \emph{Entity}, but not all entities are companies, since
some entities are \emph{Person}s - natural persons.

@@@ How to

\subsection{Migrating parts, services, ...}
\subsection{Migrating open items}
\subsection{Migrating your ledger}

\subsection{Migrating between PostgreSQL versions}

If you're migrating between PostgreSQL versions, there are a few things to take
into account.

% pg_dump: use the NEW pg_dump utility against the old database
% pg_upgrade: <TODO>
% pg_<migratecluster>: <TODO>; in case of unclean extension upgrade,
%              possible need to issue ``CREATE EXTENSION tablefunc FROM UNPACKAGED''

\subsubsection{Notes on migration from 8.3 (or earlier) to 8.4 (or later)}

% Performance benefit due to built in support for recursive queries only available
% after the next setup.pl run
% Also, after next setup.pl run, one should uninstall the tablefunc extension

% 9.1+ DROP EXTENSION tablefunc;
% 8.4, 9.0: use uninstall_tablefunc.sql from the contrib directory

LedgerSMB 1.3 uses some extension modules for versions 8.3 and before for functionality
that has been built into 8.4 and later. To make use of the (faster) built in version
of that functionality, the following restore procedure should be used.

\begin{enumerate}
\item Migrate the database to the new function as described in section @@@ TODO
\item If you're using 9.1 and up, issue the command ``CREATE EXTENSION tablefunc FROM UNPACKAGED''
   from a psql prompt when connected to the company database
\item Run 'setup.pl' from your browser to upgrade the database's routines; this command will
   install routines optimized for your version of PostgreSQL
\item Run the command
	\begin{description}
	\item [8.4 or 9.0] \$ psql ... -f uninstall\_tablefunc.sql
	\item [9.1 and up] ``DROP EXTENSION tablefunc;'' from a psql session connected
		to the company database
	\end{description}
	to clean up functions and procedures in the database which are no longer used
\end{enumerate}


\chapter{Listing of application roles}
\label{cha:RolesListing}

Application roles specify the right to execute one or more tasks in the application.
LedgerSMB enforces these roles by allowing a user to select (list, read) data from or to
insert (create), update (edit) or delete (delete) data in the tables holding the data
related to the execution of these tasks.

\begin{description}
\item [account\_all] Allows the user to both create new and edit existing GL accounts.
\item [account\_create] Allows the user to create (but not edit) new GL accounts.
\item [account\_edit] Allows the user to edit (but not create) GL accounts.
\item [ap\_all]
\item [ap\_all\_transactions]
\item [ap\_all\_vouchers]
\item [ap\_invoice\_create]
\item [ap\_invoice\_create\_voucher]
\item [ap\_transaction\_all] \footnote{Available as of 1.3.21, missing before}
\item [ap\_transaction\_create]
\item [ap\_transaction\_create\_voucher]
\item [ap\_transaction\_list]
\item [ar\_all]
\item [ar\_invoice\_create] Allows the user to create and update sales invoices. If the
   user needs to be able to enter invoices in foreign currencies, the
   \emph{exchangerate\_edit} role must be assigned as well.
\item [ar\_transaction\_all]
% just added it -- Chris T
\item [ar\_transaction\_create]
\item [ar\_transaction\_create\_voucher]
\item [ar\_transaction\_list]
\item [assembly\_stock]
\item [assets\_administer]
\item [assets\_approve]
\item [assets\_depreciate]
\item [assets\_enter]
\item [auditor]
\item [audit\_trail\_maintenance]
\item [backup] \emph{Superseeded}. This role has been replaced by backup functionality
   in setup.pl
\item [batch\_create] Allows the user to create new batches.
\item [batch\_list]
\item [batch\_post] Allows the user to post batches; this authorization includes the
   right to search for batches (and therefore includes \emph{batch\_list})
\item [business\_type\_all]
\item [business\_type\_create]
\item [business\_type\_edit]
\item [cash\_all]
\item [close\_till]
\item [contact\_all\_rights]
\item [contact\_create]
\item [contact\_edit]
\item [contact\_read]
\item [department\_all]
\item [department\_create]
\item [department\_edit]
\item [draft\_edit]
\item [employees\_manage]
\item [file\_attach\_order]
\item [file\_attach\_part]
\item [file\_attach\_tx]
\item [file\_read]
\item [financial\_reports]
\item [gifi\_create]
\item [gifi\_edit]
\item [gl\_all]
\item [gl\_reports]
\item [gl\_transaction\_create]
\item [gl\_voucher\_create]
\item [inventory\_all]
\item [inventory\_receive]
\item [inventory\_reports]
\item [inventory\_ship]
\item [inventory\_transfer]
\item [language\_create]
\item [language\_edit]
\item [list\_all\_open]
\item [manual\_translation\_all]
\item [orders\_generate]
\item [orders\_manage]
\item [orders\_purchase\_consolidate]
\item [orders\_sales\_consolidate]
\item [orders\_sales\_to\_purchase]
\item [part\_create]
\item [part\_edit]
\item [partsgroup\_translation\_create]
\item [part\_translation\_create]
\item [payment\_process]
\item [pos\_all]
\item [pos\_cashier]
\item [pos\_enter]
\item [pricegroup\_create]
\item [pricegroup\_edit]
\item [print\_jobs]
\item [print\_jobs\_list]
\item [project\_create]
\item [project\_edit]
\item [project\_order\_generate]
\item [project\_timecard\_add]
\item [project\_timecard\_list]
\item [project\_translation\_create]
\item [purchase\_order\_create]
\item [purchase\_order\_edit]
\item [purchase\_order\_list]
\item [receipt\_process]
\item [reconciliation\_all]
\item [reconciliation\_approve]
\item [reconciliation\_enter]
\item [recurring]
\item [rfq\_create]
\item [rfq\_list]
\item [sales\_order\_create]
\item [sales\_order\_edit]
\item [sales\_order\_list]
\item [sales\_quotation\_create]
\item [sales\_quotation\_list]
\item [sic\_all]
\item [sic\_create]
\item [sic\_edit]
\item [system\_admin]
\item [system\_settings\_change]
\item [system\_settings\_list]
\item [taxes\_set]
\item [tax\_form\_save]
\item [template\_edit]
\item [users\_manage]
\item [voucher\_delete]
\item [warehouse\_create]
\item [warehouse\_edit]
\item [yearend\_run]
\end{description}

\chapter{Open source explained}

\section{An open source application}

\section{An open source book}


\chapter{Copyright and license}

Copyright (c) 2011, 2012 Erik H\"ulsmann.


This work is licensed under the Creative Commons Attribution License.
To view a copy of this license, visit \url{http://creativecommons.org/licenses/by/3.0/}
or send a letter to Creative Commons, 559 Nathan Abbott Way,
Stanford, California 94305, USA.

A summary of the license is given below, followed by the full legal text.

\section{License summary}

\begin{verbatim}

You are free:
  * to share -- to copy, distribute and transmit the work
  * to remix -- to adapt the work


Under the following condition:
  You must attribute he work in the manner specified by the author or licensor
  (but in a way that suggests that they endorse you or your use of the work).


With the understanding that:
  Waiver -- Any of the above conditions can be waived if you get permission
            from the copyright holder.
  
  Other rights -- In no way are any of the following rights affected by the license:
     * Your fair dealing or fair use rights, or other applicable 
         copyright exceptions and limitations;
     * The author's moral rights;
     * Rights other persons may have either in the work itself or
         in how the work is used, such as publicity or privacy rights.



\end{verbatim}



\section{Legal full text}

\begin{verbatim}
License

THE WORK (AS DEFINED BELOW) IS PROVIDED UNDER THE TERMS OF THIS 
CREATIVE COMMONS PUBLIC LICENSE ("CCPL" OR "LICENSE"). THE WORK
IS PROTECTED BY COPYRIGHT AND/OR OTHER APPLICABLE LAW. ANY USE OF
THE WORK OTHER THAN AS AUTHORIZED UNDER THIS LICENSE OR COPYRIGHT
LAW IS PROHIBITED.

BY EXERCISING ANY RIGHTS TO THE WORK PROVIDED HERE, YOU ACCEPT AND
AGREE TO BE BOUND BY THE TERMS OF THIS LICENSE. TO THE EXTENT THIS
LICENSE MAY BE CONSIDERED TO BE A CONTRACT, THE LICENSOR GRANTS
YOU THE RIGHTS CONTAINED HERE IN CONSIDERATION OF YOUR ACCEPTANCE
OF SUCH TERMS AND CONDITIONS.

1. Definitions

"Adaptation" means a work based upon the Work, or upon the Work
and other pre-existing works, such as a translation, adaptation,
derivative work, arrangement of music or other alterations of a
literary or artistic work, or phonogram or performance and
includes cinematographic adaptations or any other form in which
the Work may be recast, transformed, or adapted including in any
form recognizably derived from the original, except that a work
that constitutes a Collection will not be considered an Adaptation
for the purpose of this License.
For the avoidance of doubt, where the Work is a musical work,
performance or phonogram, the synchronization of the Work in
timed-relation with a moving image ("synching") will be considered
an Adaptation for the purpose of this License.

"Collection" means a collection of literary or artistic works, such
as encyclopedias and anthologies, or performances, phonograms or
broadcasts, or other works or subject matter other than works
listed in Section 1(f) below, which, by reason of the selection
and arrangement of their contents, constitute intellectual
creations, in which the Work is included in its entirety in
unmodified form along with one or more other contributions, each
constituting separate and independent works in themselves, which
together are assembled into a collective whole. A work that
constitutes a Collection will not be considered an Adaptation
(as defined above) for the purposes of this License.

"Distribute" means to make available to the public the original
and copies of the Work or Adaptation, as appropriate, through sale
or other transfer of ownership.

"Licensor" means the individual, individuals, entity or entities
that offer(s) the Work under the terms of this License.

"Original Author" means, in the case of a literary or artistic
work, the individual, individuals, entity or entities who created
the Work or if no individual or entity can be identified, the
publisher; and in addition (i) in the case of a performance the
actors, singers, musicians, dancers, and other persons who act,
sing, deliver, declaim, play in, interpret or otherwise perform
literary or artistic works or expressions of folklore; (ii) in the
case of a phonogram the producer being the person or legal entity
who first fixes the sounds of a performance or other sounds; and,
(iii) in the case of broadcasts, the organization that transmits
the broadcast.

"Work" means the literary and/or artistic work offered under the
terms of this License including without limitation any production
in the literary, scientific and artistic domain, whatever may be
the mode or form of its expression including digital form, such as
a book, pamphlet and other writing; a lecture, address, sermon or
other work of the same nature; a dramatic or dramatico-musical work;
a choreographic work or entertainment in dumb show; a musical
composition with or without words; a cinematographic work to
which are assimilated works expressed by a process analogous to
cinematography; a work of drawing, painting, architecture,
sculpture, engraving or lithography; a photographic work to which
are assimilated works expressed by a process analogous to
photography; a work of applied art; an illustration, map, plan,
sketch or three-dimensional work relative to geography, topography,
architecture or science; a performance; a broadcast; a phonogram;
a compilation of data to the extent it is protected as a
copyrightable work; or a work performed by a variety or circus
performer to the extent it is not otherwise considered a literary
or artistic work.

"You" means an individual or entity exercising rights under this
License who has not previously violated the terms of this License
with respect to the Work, or who has received express permission
from the Licensor to exercise rights under this License despite
a previous violation.

"Publicly Perform" means to perform public recitations of the
Work and to communicate to the public those public recitations,
by any means or process, including by wire or wireless means or
public digital performances; to make available to the public
Works in such a way that members of the public may access these
Works from a place and at a place individually chosen by them;
to perform the Work to the public by any means or process and
the communication to the public of the performances of the Work,
including by public digital performance; to broadcast and
rebroadcast the Work by any means including signs, sounds or
images.

"Reproduce" means to make copies of the Work by any means
including without limitation by sound or visual recordings and
the right of fixation and reproducing fixations of the Work,
including storage of a protected performance or phonogram in
digital form or other electronic medium.

2. Fair Dealing Rights. Nothing in this License is intended to
reduce, limit, or restrict any uses free from copyright or rights
arising from limitations or exceptions that are provided for in
connection with the copyright protection under copyright law or
other applicable laws.

3. License Grant. Subject to the terms and conditions of this License,
Licensor hereby grants You a worldwide, royalty-free, non-exclusive,
perpetual (for the duration of the applicable copyright) license to
exercise the rights in the Work as stated below:

to Reproduce the Work, to incorporate the Work into one or more
Collections, and to Reproduce the Work as incorporated in the
Collections;
to create and Reproduce Adaptations provided that any such
Adaptation, including any translation in any medium, takes
reasonable steps to clearly label, demarcate or otherwise identify
that changes were made to the original Work. For example, a
translation could be marked "The original work was translated from
English to Spanish," or a modification could indicate "The
original work has been modified.";
to Distribute and Publicly Perform the Work including as
incorporated in Collections; and,
to Distribute and Publicly Perform Adaptations.
For the avoidance of doubt:

Non-waivable Compulsory License Schemes. In those jurisdictions
in which the right to collect royalties through any statutory
or compulsory licensing scheme cannot be waived, the Licensor
reserves the exclusive right to collect such royalties for any
exercise by You of the rights granted under this License;
Waivable Compulsory License Schemes. In those jurisdictions in
which the right to collect royalties through any statutory or
compulsory licensing scheme can be waived, the Licensor waives
the exclusive right to collect such royalties for any exercise
by You of the rights granted under this License; and,
Voluntary License Schemes. The Licensor waives the right to
collect royalties, whether individually or, in the event that
the Licensor is a member of a collecting society that
administers voluntary licensing schemes, via that society, from
any exercise by You of the rights granted under this License.
The above rights may be exercised in all media and formats
whether now known or hereafter devised. The above rights include
the right to make such modifications as are technically
necessary to exercise the rights in other media and formats.
Subject to Section 8(f), all rights not expressly granted by
Licensor are hereby reserved.

4. Restrictions. The license granted in Section 3 above is
expressly made subject to and limited by the following
restrictions:

You may Distribute or Publicly Perform the Work only under
the terms of this License. You must include a copy of, or the
Uniform Resource Identifier (URI) for, this License with every
copy of the Work You Distribute or Publicly Perform. You may
not offer or impose any terms on the Work that restrict the
terms of this License or the ability of the recipient of the
Work to exercise the rights granted to that recipient under
the terms of the License. You may not sublicense the Work. You
must keep intact all notices that refer to this License and to
the disclaimer of warranties with every copy of the Work You
Distribute or Publicly Perform. When You Distribute or Publicly
Perform the Work, You may not impose any effective technological
measures on the Work that restrict the ability of a recipient
of the Work from You to exercise the rights granted to that
recipient under the terms of the License. This Section 4(a)
applies to the Work as incorporated in a Collection, but this
does not require the Collection apart from the Work itself to
be made subject to the terms of this License. If You create
a Collection, upon notice from any Licensor You must, to the
extent practicable, remove from the Collection any credit as
required by Section 4(b), as requested. If You create an
Adaptation, upon notice from any Licensor You must, to the
extent practicable, remove from the Adaptation any credit as
required by Section 4(b), as requested.
If You Distribute, or Publicly Perform the Work or any
Adaptations or Collections, You must, unless a request has
been made pursuant to Section 4(a), keep intact all copyright
notices for the Work and provide, reasonable to the medium or
means You are utilizing: (i) the name of the Original Author
(or pseudonym, if applicable) if supplied, and/or if the
Original Author and/or Licensor designate another party or
parties (e.g., a sponsor institute, publishing entity,
journal) for attribution ("Attribution Parties") in Licensor's
copyright notice, terms of service or by other reasonable
means, the name of such party or parties; (ii) the title of
the Work if supplied; (iii) to the extent reasonably
practicable, the URI, if any, that Licensor specifies to be
associated with the Work, unless such URI does not refer to the
copyright notice or licensing information for the Work;
and (iv) , consistent with Section 3(b), in the case of an
Adaptation, a credit identifying the use of the Work in the
Adaptation (e.g., "French translation of the Work by Original
Author," or "Screenplay based on original Work by Original
Author"). The credit required by this Section 4 (b) may be
implemented in any reasonable manner; provided, however, that
in the case of a Adaptation or Collection, at a minimum such
credit will appear, if a credit for all contributing authors
of the Adaptation or Collection appears, then as part of these
credits and in a manner at least as prominent as the credits
for the other contributing authors. For the avoidance of doubt,
You may only use the credit required by this Section for the
purpose of attribution in the manner set out above and, by
exercising Your rights under this License, You may not
implicitly or explicitly assert or imply any connection
with, sponsorship or endorsement by the Original Author,
Licensor and/or Attribution Parties, as appropriate, of
You or Your use of the Work, without the separate, express
prior written permission of the Original Author, Licensor
and/or Attribution Parties.
Except as otherwise agreed in writing by the Licensor or as
may be otherwise permitted by applicable law, if You Reproduce,
Distribute or Publicly Perform the Work either by itself or
as part of any Adaptations or Collections, You must not distort,
mutilate, modify or take other derogatory action in relation to
the Work which would be prejudicial to the Original Author's
honor or reputation. Licensor agrees that in those
jurisdictions (e.g. Japan), in which any exercise of the right
granted in Section 3(b) of this License (the right to make
Adaptations) would be deemed to be a distortion, mutilation,
modification or other derogatory action prejudicial to the
Original Author's honor and reputation, the Licensor will
waive or not assert, as appropriate, this Section, to the
fullest extent permitted by the applicable national law, to
enable You to reasonably exercise Your right under
Section 3(b) of this License (right to make Adaptations)
but not otherwise.

5. Representations, Warranties and Disclaimer

UNLESS OTHERWISE MUTUALLY AGREED TO BY THE PARTIES IN WRITING,
LICENSOR OFFERS THE WORK AS-IS AND MAKES NO REPRESENTATIONS
OR WARRANTIES OF ANY KIND CONCERNING THE WORK, EXPRESS,
IMPLIED, STATUTORY OR OTHERWISE, INCLUDING, WITHOUT
LIMITATION, WARRANTIES OF TITLE, MERCHANTIBILITY, FITNESS FOR
A PARTICULAR PURPOSE, NONINFRINGEMENT, OR THE ABSENCE OF
LATENT OR OTHER DEFECTS, ACCURACY, OR THE PRESENCE OF ABSENCE
OF ERRORS, WHETHER OR NOT DISCOVERABLE. SOME JURISDICTIONS DO
NOT ALLOW THE EXCLUSION OF IMPLIED WARRANTIES, SO SUCH
EXCLUSION MAY NOT APPLY TO YOU.

6. Limitation on Liability.

EXCEPT TO THE EXTENT REQUIRED BY APPLICABLE LAW, IN NO EVENT
WILL LICENSOR BE LIABLE TO YOU ON ANY LEGAL THEORY FOR ANY
SPECIAL, INCIDENTAL, CONSEQUENTIAL, PUNITIVE OR EXEMPLARY
DAMAGES ARISING OUT OF THIS LICENSE OR THE USE OF THE WORK,
EVEN IF LICENSOR HAS BEEN ADVISED OF THE POSSIBILITY OF SUCH
DAMAGES.

7. Termination

This License and the rights granted hereunder will terminate
automatically upon any breach by You of the terms of this
License. Individuals or entities who have received Adaptations
or Collections from You under this License, however, will not
have their licenses terminated provided such individuals
or entities remain in full compliance with those licenses.
Sections 1, 2, 5, 6, 7, and 8 will survive any termination
of this License. Subject to the above terms and conditions,
the license granted here is perpetual (for the duration of
the applicable copyright in the Work). Notwithstanding the
above, Licensor reserves the right to release the Work under
different license terms or to stop distributing the Work at
any time; provided, however that any such election will not
serve to withdraw this License (or any other license that has
been, or is required to be, granted under the terms of this
License), and this License will continue in full force and
effect unless terminated as stated above.

8. Miscellaneous

Each time You Distribute or Publicly Perform the Work or a
Collection, the Licensor offers to the recipient a license
to the Work on the same terms and conditions as the license
granted to You under this License. Each time You Distribute
or Publicly Perform an Adaptation, Licensor offers to the
recipient a license to the original Work on the same terms and
conditions as the license granted to You under this License.
If any provision of this License is invalid or unenforceable
under applicable law, it shall not affect the validity or
enforceability of the remainder of the terms of this License,
and without further action by the parties to this agreement,
such provision shall be reformed to the minimum extent
necessary to make such provision valid and enforceable.
No term or provision of this License shall be deemed waived
and no breach consented to unless such waiver or consent shall
be in writing and signed by the party to be charged with
such waiver or consent.
This License constitutes the entire agreement between the
parties with respect to the Work licensed here. There are
no understandings, agreements or representations with respect
to the Work not specified here. Licensor shall not be bound
by any additional provisions that may appear in any
communication from You. This License may not be modified
without the mutual written agreement of the Licensor and You.
The rights granted under, and the subject matter referenced,
in this License were drafted utilizing the terminology of the
Berne Convention for the Protection of Literary and Artistic
Works (as amended on September 28, 1979), the Rome Convention
of 1961, the WIPO Copyright Treaty of 1996, the WIPO
Performances and Phonograms Treaty of 1996 and the Universal
Copyright Convention (as revised on July 24, 1971). These
rights and subject matter take effect in the relevant
jurisdiction in which the License terms are sought to be
enforced according to the corresponding provisions of the
implementation of those treaty provisions in the applicable
national law. If the standard suite of rights granted under
applicable copyright law includes additional rights not
granted under this License, such additional rights are deemed
to be included in the License; this License is not intended
to restrict the license of any rights under applicable law.

\end{verbatim}

