% !TeX encoding = UTF-8
% !TeX spellcheck = en_US

\documentclass[10pt,a4paper]{book}

\usepackage{url, palatino, color}
\usepackage[colorlinks, linkcolor=black, urlcolor=black]{hyperref}
\usepackage{graphicx}
\usepackage{longtable}
\graphicspath{{images/}}

% glossaries must be loaded *after* hyperref
\usepackage[acronym]{glossaries}
\makeglossaries

\ifdefined\LaTeXML
  \newcommand{\figref}[1]{Figure~\ref{#1}}
  \newcommand{\tabref}[1]{Table~\ref{#1}}
  \newcommand{\secref}[1]{Section~\ref{#1}}
  \newcommand{\charef}[1]{Chapter~\ref{#1}}
  \newcommand{\appref}[1]{Appendix~\ref{#1}}
\else
  \newcommand{\figref}[1]{Figure~\ref{#1} on page~\pageref{#1}}
  \newcommand{\tabref}[1]{Table~\ref{#1} on page~\pageref{#1}}
  \newcommand{\secref}[1]{Section~\ref{#1} on page~\pageref{#1}}
  \newcommand{\charef}[1]{Chapter~\ref{#1} starting at page~\pageref{#1}}
  \newcommand{\appref}[1]{Appendix~\ref{#1} starting at page~\pageref{#1}}
\fi

\newcommand{\menupath}[1]{{\tt #1}}
\newcommand{\ma}{\ensuremath{\rightarrow}}


\begin{document}
\include{acronyms}
\include{glossary}


\author{Erik H\"ulsmann, Chris Travers}
\title{\begin{Large}
Running your business with
\end{Large} \\
LedgerSMB 1.3 \\
 ~ \\
\texttt{DRAFT / WORK IN PROGRESS} }


\maketitle


\tableofcontents

\listoffigures

\listoftables

\printglossaries

\chapter*{Preface}
\label{preface}

\section*{Intended audience}
\label{sec-intended-audience}

The book has been split up in several parts intended for starting entrepreneurs,
(potential) users, application integration developers and
administrators, it offers something for everybody who works with or considers working with
LedgerSMB.

\section*{Organization of the book}
\label{sec-book-organization}

The first
part ('Overview') is intended for everybody who tries to get an impression of LedgerSMB, with
chapters on technology, features, licensing and a bit of project history.

The second part
('Getting started') leads new users and especially new entrepreneurs step by step through the
application. This part also contains additional explanations on good business and accounting
process.

The third part ('Configuration') describes system wide configuration settings such as
the LedgerSMB configuration file and those required for dependencies like PostgreSQL. Additionally
it describes the company specific settings within the application, such as audit control settings
and required special accounts. This part is required material for anybody who wants to set up
a LedgerSMB instance.

The fourth part ('Administration') discusses the different topics
regarding application administration such as user management, product definition, taxes and etc.
Anybody responsible for maintaining application instances in good health should read this part.

The fifth part discusses work flows; LedgerSMB best practices, so to say. This part is highly advised
reading for everybody who is a LedgerSMB user and should be considered required reading for 'business
architects': those in the company who decide about process design and execution.

The sixth part discusses how to customize the application. This part is intended for developers of
custom extensions (such as company specific integrations), add-ons and plug-ins.

The last part, the appendices, contain information on various subjects, such as a listing and description
of the authorization roles in the application as well as information on migration to or upgrading of
LedgerSMB versions.


\section*{Comments and questions}
\label{sec-comments}

The sources of this book are being developed in the ledgersmb-book Google Code project at
\url{https://code.google.com/p/ledgersmb-book/}. Comments and enhancement ideas can be filed
in the ticket tracker of the project. Additionally, discussion about the content of the book
can be organized on the IRC freenode.net channel \#ledgersmb or the ledger-smb-devel for which
you can subscribe at \url{https://lists.sourceforge.net/lists/listinfo/ledger-smb-devel}.



\section*{Acknowledgements}
\label{sec-acknowledgements}

H{\aa}vard S{\o}rli for his efforts to help out develop the book outline.

\include{part-overview}
\include{part-getting-started}
\include{part-configuration}
\include{part-administration}
\include{part-workflows}
\include{part-customization}
\include{appendices}




\end{document}

